---
title: "eds221-morning"
format: html
editor: visual
---

## Functions

```{r}
double_value <- function(my_dollars) {
  print(2 * my_dollars)
}

double_value(10.13)
```

```{r}
monthly_income <- c(42, 50, 61.75, 89.50)

double_value(monthly_income)
```

Create a function that returns an awesome restaurant name given a cool animal and your favorite food.

```{r}
name_rest <- function(animal, food) {
  print(paste0(animal, food))
}

name_rest(animal = "hawk", food = "pizza")
```

Given a temperature in degrees (F), write a function that converts it to Celsius.

```{r}

convert_f_to_c <- function(temp_f) {
  print((temp_f - 32) * (5 / 9))
}

convert_f_to_c(temp_f = 52)
```

Create a function that given inputs of age and hometown, returns "I am \_ years old, and I'm from\_"

```{r}
age_hometown <- function(age, hometown) {
  print(paste("I am", age, "years old", "and I'm from", hometown))
}

age_hometown(age = 25, hometown = "Bakersfield")
```

```{r}
#You dont always need to put print at the end of the function 
double_value2 <- function(dollars) {
  dollars * 2
}

double_value2(dollars = 10)
```

Print statements and return statements

print: "show me"

return: store this so I can use it later

## Functions with conditionals

```{r}
calculate_animal_age <- function(species, age_human_yr) {
  if (species  == "dog") {
    print(age_human_yr * 7)
   } else if (species == "goat") {
      print(age_human_yr * 4.7)
   } else {
    print("Please enter dog or goat")
  }
}
```

```{r}
calculate_animal_age(species = "dog", age_human_yr = 10)

calculate_animal_age(species = "goat", age_human_yr = 4)
```

Write a function that, given temp in Kelvin, if a user selects "metric" to the scale then return degrees Celsius, or if they select "english" then return in degrees F.

```{r}
tempk_convert <- function(scale, temp_k) {
  if (scale == "metric") {
    print(temp_k - 273.15)
  } else if(scale == "english") {
    print(((temp_k - 273.15) * 1.8) + 32)
  }
}

my_value <- tempk_convert(scale = "metric", temp_k = 47)
```
